% Supplementary data inventory table synchronized with the release package.
% Paths are relative to the archive root scirep_lbm_swarm_submission_package/.
{\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{longtable}{@{}>{\RaggedRight\arraybackslash}p{0.40\linewidth}>{\RaggedRight\arraybackslash}p{0.55\linewidth}@{}}
\caption{Supplementary data and reproducibility inventory. Paths are relative to the archive root \texttt{scirep\_lbm\_swarm\_submission\_package/} and are synchronized with the GitHub/Zenodo DOI-synchronized release at https://doi.org/10.5281/zenodo.21211257.}\label{stab:source-data-inventory}\\
\toprule
File or folder in archive & Purpose \\
\midrule
\endfirsthead
\toprule
File or folder in archive & Purpose \\
\midrule
\endhead
\bottomrule
\endfoot

\begin{tabular}[t]{@{}l@{}}\texttt{config/}\\\texttt{production\_config.json}\end{tabular}
& Final production configuration: grids, density parameters, agent counts, 100 stable runs per condition, $r_i=5.0$, $m_i=25.0$, nearest-node forcing, and $v_{0,\max}=0.2$. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/tables/}\\\texttt{master\_attempt\_log.csv}\end{tabular}
& Per-attempt stability status, seed, stopping reason, raw detections, unique events, final active contacts, maximum density, and maximum velocity. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/tables/}\\\texttt{scirep\_condition\_summary}\\\texttt{\_raw\_unique\_stability.csv}\end{tabular}
& Processed condition-level summary used to build endpoint, raw/unique contact, and stability tables reported in the manuscript and Supplementary Information. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/tables/}\\\texttt{scirep\_stability}\\\texttt{\_audit\_table.csv}\end{tabular}
& Compact stability audit table aggregating stable runs, unstable attempts, maximum density, and maximum velocity by grid and density parameter. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/tables/}\\\texttt{scirep\_time\_series\_summary}\\\texttt{\_by\_condition\_step.csv}\end{tabular}
& Processed time-series summaries by condition and step for contact accumulation, active-contact, maximum-density, and stability curves. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/tables/}\\\texttt{scirep\_run\_level}\\\texttt{\_transient\_metrics.csv}\end{tabular}
& Run-level transient metrics derived from per-step histories. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/tables/}\\\texttt{scirep\_transient}\\\texttt{\_metrics\_summary.csv/.tex}\end{tabular}
& Summary of transient metrics used for supplementary reporting and audit checks. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/tables/}\\\texttt{count\_model\_coefficients.csv}\\\texttt{count\_model\_status.txt}\end{tabular}
& Exploratory count-model coefficients and status notes. These files are included for auditability only and are not used as central statistical evidence. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/tables/}\\\texttt{scirep\_quadratic\_fit\_table}\\\texttt{\_raw\_detections.tex}\\\texttt{scirep\_quadratic\_fit\_table}\\\texttt{\_unique\_events.tex}\end{tabular}
& Descriptive quadratic-fit source tables used for supplementary trend summaries. \\
\addlinespace[0.35em]

\texttt{source\_data/figures/}
& Selected PDF figure-source files corresponding to the main-manuscript visual results. \\
\addlinespace[0.35em]

\texttt{source\_data/supplementary\_figures/}
& Selected PDF figure-source files corresponding to Supplementary Figs. S1--S8. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/supplementary\_tables/}\\\texttt{supplementary\_table\_S12}\\\texttt{\_compact\_sensitivity.csv/.tex}\end{tabular}
& Compact matched-seed sensitivity audit around proxy mass, force-spreading rule, and velocity-clamp scale. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{source\_data/supplementary\_tables/}\\\texttt{compact\_sensitivity\_attempt\_logs/}\end{tabular}
& Per-variant attempt logs for the compact sensitivity audit. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{src/}\\\texttt{lbm\_swarm\_contact\_simulator.py}\end{tabular}
& Main simulation script producing raw repeated detections, de-duplicated unique contact events, stability logs, per-run summaries, and per-step time-series outputs. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{src/}\\\texttt{lbm\_swarm\_contact\_simulator}\\\texttt{\_sensitivity.py}\end{tabular}
& Compact-sensitivity simulator variant with pre-clamp speed and clamp-activation diagnostics. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{src/}\\\texttt{scirep\_generate\_tables\_figures.py}\end{tabular}
& Analysis and plotting script used to generate manuscript tables, supplementary tables, figures, and processed source-data summaries from completed simulation outputs. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{src/}\\\texttt{validate\_submitted\_source\_data.py}\end{tabular}
& Validator for the compact source-data files included in this release. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{scripts/}\\\texttt{00\_create\_environment.sh}\\\texttt{...}\\\texttt{07\_make\_checksums.sh}\end{tabular}
& Reproduction helper scripts for environment creation, smoke tests, mass screening, design checks, production reruns, validation, analysis, and checksum generation. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{manuscript\_support/}\\\texttt{main\_scientific\_reports}\\\texttt{\_release\_ready.pdf/.tex}\end{tabular}
& Manuscript-support snapshot bundled with this DOI-synchronized release and citing the archive DOI https://doi.org/10.5281/zenodo.21211257. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{manuscript\_support/}\\\texttt{Supplementary\_Material}\\\texttt{\_release\_ready.pdf/.tex}\end{tabular}
& Supplementary Information synchronized with the DOI-synchronized release package at https://doi.org/10.5281/zenodo.21211257, including this inventory and Supplementary Table S12. \\
\addlinespace[0.35em]

\begin{tabular}[t]{@{}l@{}}\texttt{README.md}, \texttt{requirements.txt},\\\texttt{environment.yml}, \texttt{CITATION.cff},\\\texttt{.zenodo.json}, \texttt{LICENSE},\\\texttt{DATA\_LICENSE.txt}, \texttt{MANIFEST.tsv},\\\texttt{checksums\_sha256.txt}\end{tabular}
& Repository-level instructions, software environment files, citation and Zenodo metadata, license files, file manifest, and checksum manifest. \\

\end{longtable}
}
